int-theory-vacc: Study 2 modeling

### 2019-08-08 notebooks/cross-study-analysis.Rmd
before paper reorg

s4 <- df4 %>%
  mutate(prior_study = case_when(
    workerId %in% s1$workerId ~ "S1",
    workerId %in% s3$workerId ~ "S3",
    TRUE ~ "None"
  )) %>%
  mutate(resp = resp-4) %>%
  filter(prior_study != "S3") %>% # exclude Ps from s3, some of whom saw intervention
  group_by(scale, workerId) %>%
  summarize(s4 = mean(resp))
```

@@

df_studies <-  s1 %>%
  full_join(s2) %>%
  # full_join(s3) %>%
  full_join(s4) %>%
  gather(study, score, -c(workerId, scale)) %>%
  filter(!is.na(study), !is.na(score)) %>%
  group_by(scale) %>%
  mutate(score_std = scale(score, scale = T)) %>%
  ungroup()
```

@@

```{r}
studies_plot <- df_studies %>%
  group_by(study, scale) %>%
  summarize(
    mean = mean(score),
    se = sd(score)/sqrt(n()),
    ul = mean + se,
    ll = mean - se,
    ul95 = mean + 1.96*se,
    ll95 = mean - 1.96*se
  ) %>%
  ungroup() %>%
  mutate(study = ordered(study, labels=c("S1\n(9/17)", "S2\n(5/18)","S3\n(5/19)"))) %>%
  mutate(scale = recode_factor(
    scale,
    "vaccIntent" = "Vaccination\nIntentions",
    "nat" = "Naturalism",
    "hb" = "Holistic Balance",
    "overpar" = "Parental\nProtectiveness",
    "parentExpert" = "Parental Expertise",
    "medSkept" = "Medical Skepticism",
    "vaccDanger" = "Vaccine Danger",
    "vaccTox" = "Vaccine Toxicity",
    "vaccEff" = "Vaccine Efficacy",
    "diseaseRare" = "Disease Rarity",
    "diseaseSevere" = "Disease Severity",
    "infantImmWeak" = "IIS:\nWeakness",
    "infantImmLimCap" = "IIS:\nLimited Capacity",
    "vaccStrain" = "IIS:\nVaccines Strain")) %>%
  ggplot(aes(x=study, y = mean, ymin =ll, ymax=ul)) +
  # geom_pointrange() +
  geom_point(size=2.5, shape=16) +
  geom_errorbar(size=1, width=0, alpha=.8) +
  geom_errorbar(aes(ymin=ll95, ymax = ul95), width=0, alpha=.5) +
  facet_wrap(~scale, scales="free", nrow = 2) +
  theme_bw(base_size = 16) +
  theme(
    # legend.position = "bottom",
    # axis.text.x = element_text(size=8),
    panel.grid = element_blank()
        ) +
  labs(y="Mean Resposne", x = "Study")

ggsave("../local/uci-longitudinal-averages.png",studies_plot, height=8, width=16)
```

@@

# combined %>%
#   filter(returned == TRUE) %>%
#   ggplot(aes(x=pretest, y=posttest)) +
#   geom_jitter(alpha=.5) +
#   facet_wrap(~scale) +
#   theme_bw()

@@

combined_long %>%
  group_by(returned, phase, scale) %>%
  summarize(
    mean = mean(resp),
    se = sd(resp)/sqrt(n()),
    ul = mean + se,
    ll = mean - se,
    ul95 = mean + 1.96*se,
    ll95 = mean - 1.96*se
  ) %>%
  ungroup() %>%
  mutate(scale = recode_factor(
  scale,
  "vaccIntent" = "Vaccination Intentions",
  "nat" = "Naturalism",
  "hb" = "Holistic Balance",
  "overpar" = "Parental Protectiveness",
  "parentExpert" = "Parental Expertise",
  "medSkept" = "Medical Skepticism",
  "vaccDanger" = "Vaccine Danger",
  "vaccTox" = "Vaccine Toxicity",
  "vaccEff" = "Vaccine Efficacy",
  "diseaseRare" = "Disease Rarity",
  "diseaseSevere" = "Disease Severity",
  "infantImmWeak" = "IIS: Weakness",
  "infantImmLimCap" = "IIS: Limited Capacity",
  "vaccStrain" = "IIS: Vaccines Strain")) %>%
  mutate(phase = ordered(phase, levels=c("pretest","posttest"))) %>%
  ggplot(aes(x=phase, y = mean, ymin =ll, ymax=ul, color=returned)) +
  geom_point(position=position_dodge(width=.25), size=2, shape=16) +
  geom_errorbar(position=position_dodge(width=.25), size=.75, width=0, alpha=.8) +
  geom_errorbar(aes(ymin=ll95, ymax = ul95), width=0, position=position_dodge(width=.25), alpha=.5) +
  facet_wrap(~scale, scales="free") +
  theme_bw(base_size=18)

change_plot <- combined %>%
  filter(returned==TRUE) %>%
  mutate(diff = posttest-pretest) %>%
  mutate(scale = recode_factor(
    scale,
    "vaccIntent" = "Vaccination Intentions",
    "nat" = "Naturalism",
    "hb" = "Holistic Balance",
    "overpar" = "Parental Protectiveness",
    "parentExpert" = "Parental Expertise",
    "medSkept" = "Medical Skepticism",
    "vaccDanger" = "Vaccine Danger",
    "vaccTox" = "Vaccine Toxicity",
    "vaccEff" = "Vaccine Efficacy",
    "diseaseRare" = "Disease Rarity",
    "diseaseSevere" = "Disease Severity",
    "infantImmWeak" = "IIS: Weakness",
    "infantImmLimCap" = "IIS: Limited Capacity",
    "vaccStrain" = "IIS: Vaccines Strain")) %>%
  group_by(scale) %>%
  summarize(
    mean = mean(diff),
    se = sd(diff)/sqrt(n()),
    ul = mean + se,
    ll = mean - se,
    ul95 = mean + 1.96*se,
    ll95 = mean - 1.96*se
  ) %>%
  ungroup() %>%
  # mutate(phase = ordered(phase, levels=c("pretest","posttest"))) %>%
  ggplot(aes(x=reorder(scale, -mean), y = mean, ymin =ll, ymax=ul)) +
  geom_point(position=position_dodge(width=.25), size=2, shape=16) +
  geom_errorbar(position=position_dodge(width=.25), size=.75, width=0, alpha=.8) +
  geom_errorbar(aes(ymin=ll95, ymax = ul95), width=0, position=position_dodge(width=.25), alpha=.5) +
  geom_hline(yintercept = 0, linetype="dashed",alpha=.5) +
  # facet_wrap(~scale, scales="free") +
  theme_bw(base_size = 18) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  theme(
    panel.grid = element_blank()
        ) +
  labs(y = "Change scores", x = "Belief scale")

ggsave("../local/uci-longitudinal-changescores.png",change_plot, height=6, width=8)
```

```{r}
# diff_df <- combined %>% 
#   group_by(scale) %>% 
#   summarize(posttest = mean(posttest, na.rm=TRUE), 
#             pretest=mean(pretest)) %>% 
#   mutate(diff = posttest-pretest)

diff_df <- combined %>%
  filter(returned == TRUE) %>%
  mutate(difference = posttest-pretest) %>%
  group_by(scale) %>%
  summarize(diff = mean(difference), se = sd(difference)/sqrt(n()))

@@

change_cors %>%
  ggplot(aes(y=reorder(scale, corr), x = corr)) +
  geom_point() +
  theme_bw(base_size=18) +
  theme(aspect.ratio=1) +
  theme(panel.grid = element_blank())
  labs(y="Scale", x = "Correlation")
```

@@

plot_cohere <- z %>%
  ggplot(aes(x=pred_diff, y=diff, ymin=diff-1.96*se, ymax=diff+1.96*se)) +
  geom_errorbar(width=0, color="grey") +
  geom_point() +
  geom_abline(intercept = 0, slope=1, linetype="dashed",alpha=.5) +
  theme_bw(base_size=18) +
  theme(aspect.ratio=1) +
  coord_cartesian(xlim=c(-.32,.32), ylim=c(-.32,.32)) +
  theme(panel.grid=element_blank()) +
  labs(x="Predicted change",y="Observed change")

# ggsave("../local/uci-talk-cohere.png", width=4, height=4)
cor(z$pred_diff, z$diff)
plot_cohere
```

@@

# Actually predicting using the model ...

```{r}
## WARNING: THIS CODE IS HACKY!
## 
## script for generating model predictions based on vaccine toxins intervention
## run:
## int-theory-vacc/notebooks/s2-modeling.Rmd (to line 495)
##
## then run this notebook, and finally this code:

d_scored_longitudinal <- combined_long %>%
  filter(returned==TRUE) %>%
  mutate(resp = rescale_beta(resp, -3, 3)) %>%
  group_by(phase, scale) %>%
  summarize(mean = mean(resp)) %>%
  spread(phase,mean) %>%
  rename(pre = pretest, post = posttest)

# # update model fitting thing ignore control condition b/c of strange things in this data ...
find_evid_ratio <- function(data){
    optim(par = c(0), fn = evid_score_func, data = data, method="BFGS")
}
# find_evid_ratio <- function(data){
#   # HACK HACK HACK
#   return (data.frame(par = c(-.55, 7)))
# }
evid_score_func <- function(data, par) {

    inv_logit <- plogis
    logit <- qlogis

    pred_y <- with(data,
                   {
                       inv_logit( logit(pre) + par[1] )
                   }
    )

    # pred_beta_A <- pred_y * par[2]
    # pred_beta_B <- (1-pred_y) * par[2]

    # ll <- -1 * sum(dbeta(data$post, pred_beta_A, pred_beta_B, log=TRUE)) # beta regression
    ll <- sum( (data$post-pred_y)^2 )
    return(ll)
}

get_evid_probs <- function(result){
  # this is a heuristic/hack, could be made better but probably doesn't matter
  evid_ratio <- exp(result$par[1])
  if (evid_ratio < 1) {
    p0 <- .90
  } else {
    p0 <- .5
  }

  if (p0*evid_ratio >= 1) {
    p0 <- p0*.9/(p0*evid_ratio)
  }
  p1 <- p0*evid_ratio

  c(p0,p1)
}

scale_name <- "vaccIntent"

predModel <- add_evid_node(d_scored_longitudinal %>% filter(scale==scale_name), base_model, scale_name)

pred0 <- sapply(nodes, function(x){
  statement <- paste0("cpquery(predModel, event = (", x, " == 'Yes'), evidence=TRUE, n = 5e5)")
  eval(parse(text=statement))
})
pred1 <- sapply(nodes, function(x){
  statement <- paste0("cpquery(predModel, event = (", x, " == 'Yes'), evidence= (evid == 'Yes'), n = 5e5)")
  eval(parse(text=statement))
})
pred_changes <- pred1 - pred0
pred_changes <- as.data.frame(pred_changes)
pred_changes <- pred_changes %>%
  mutate(scale = nodes) %>%
  rename(Mean = pred_changes) %>%
  mutate(type = "predicted")

preds_obs <- d_scored_longitudinal %>%
  # spread(phase, mean) %>%
  mutate(change = post - pre) %>%
  group_by(scale) %>%
  summarize(
    Mean = mean(change),
    se = sd(change) / sqrt(n())
  ) %>%
  mutate(
    ul = Mean + se,
    ll = Mean - se
  ) %>%
  left_join(pred_changes %>% rename(pred_mean = Mean), by = "scale")

preds_obs %>%
  rename(
    observed = Mean,
    predicted = pred_mean
  ) %>%
  gather(type, Mean, observed, predicted) %>%
  ggplot(aes(y = reorder(scale, Mean), x = Mean, xmin = ll, xmax = ul, color=type)) +
  geom_point()
```

```{r}
diff_df2 <- combined %>%
  filter(returned == TRUE) %>%
  mutate(
    posttest = rescale_beta(posttest, -3,3),
    pretest = rescale_beta(pretest, -3,3),
         ) %>%
  mutate(difference = posttest-pretest) %>%
  group_by(scale) %>%
  summarize(diff = mean(difference), se = sd(difference)/sqrt(n()))

plot_cohere <- diff_df2 %>%
  left_join(preds_obs %>% select(pred_mean, scale)) %>%
  ggplot(aes(x=pred_mean, y = diff, ymin = diff-1.96*se, ymax=diff+1.96*se)) +
  geom_errorbar(width=0, color="gray") +
  geom_point() +
  geom_abline(intercept=0,slope=1,alpha=.5,linetype="dashed") +
  theme_bw() +
  coord_cartesian(xlim=c(-.06,.06), ylim= c(-.06,.06)) +
  theme_bw(base_size=16) +
  theme(aspect.ratio=1, panel.grid=element_blank()) +
  labs(x = "Predicted change", y = "Observed change")

cor(preds_obs$Mean, preds_obs$pred_mean)

ggsave("../local/fb-talk-cohere.png", width=4, height=4)

pred_check <- preds_obs %>% filter(scale!=scale_name)
cor(pred_check$Mean, pred_check$pred_mean)

plot_cohere
```

```{r}
# plot_cohere <- preds_obs %>%
#   ggplot(aes(x=pred_mean, y = Mean, ymin = ll, ymax=ul)) +
#   geom_point() +
#   geom_errorbar(width=0) +
#   geom_abline(intercept=0,slope=1,alpha=.5,linetype="dashed") +
#   theme_bw() +
#   coord_cartesian(xlim=c(-.05,.05), ylim= c(-.05,.05)) +
#   theme_bw(base_size=16) +
#   theme(aspect.ratio=1, panel.grid=element_blank()) +
#   labs(x = "Predicted change", y = "Observed change")
# 
# cor(preds_obs$Mean, preds_obs$pred_mean)
# 
# # ggsave("../local/uci-talk-cohere.png", width=4, height=4)
# 
# pred_check <- preds_obs %>% filter(scale!=scale_name)
# cor(pred_check$Mean, pred_check$pred_mean)

# plot_cohere
```

```{r}
# needed for next section
base_model <- create_bnlearn_cog_model(map_dag, train)
```

```{r}
compare_pred_obs_r <- function(predicted, observed){

  obs_pred <- suppressWarnings(bind_rows(predicted, observed)) %>%
    spread(type, Mean) %>%
    group_by(scale) %>%
    summarize_all(mean, na.rm=TRUE)

  cor(obs_pred$predicted, obs_pred$observed)
}

compare_pred_obs_rmse <- function(predicted, observed){

  obs_pred <- suppressWarnings(bind_rows(predicted, observed)) %>%
    spread(type, Mean) %>%
    group_by(scale) %>%
    summarize_all(mean, na.rm=TRUE)

  sqrt(mean((obs_pred$observed-obs_pred$predicted)^2))

}

extract_obs_changes <- function(observed){
  obs_changes <- observed %>%
  mutate(mean = rescale_beta(mean, -3, 3)) %>%
  spread(phase,mean) %>%
  mutate(changeScore = posttest-pretest) %>%
  # filter(condition == "diseaseRisk") %>%
  group_by(scale) %>%
  summarise(
    Mean = mean(changeScore),
    ul = mean(changeScore) + 1.96*sd(changeScore)/sqrt(n()), # replace with bootstrapping
    ll = mean(changeScore) - 1.96*sd(changeScore)/sqrt(n())
    ) %>%
  mutate(type = "observed")

  return(obs_changes)
}

combined_long_diag <- combined_long %>%
  filter(returned) %>%
  rename(mean = resp)

filter_dscored <- function(data, scale_name){

  data %>%
  filter(scale == scale_name) %>%
  mutate(mean = rescale_beta(mean, -3, 3)) %>%
  spread(phase, mean) %>%
  # rename(pre=pretest, post=posttest)
  summarize(pre = mean(pretest), post=mean(posttest))
}

# -- takes about 1.5 hrs for 500 bootstrap samples

# do bootstrap comparison
set.seed(1234)
t1 <- Sys.time()

boot_fits <- as_tibble(expand.grid(
  list(
    replicate = 1:100, scale = nodes
  )
)) %>%
  nest(-replicate, .key="scales") %>%
  mutate(boot_d_scored = map(replicate, function(x) {
    totaln <- length(unique(combined_long_diag$workerId))
    combined_long_diag %>%
      nest(-workerId) %>%
      sample_n(totaln, replace = TRUE) %>%
      mutate(uniqueId = 1:totaln) %>%
      unnest()
  })) %>%
  unnest(scales, .drop=FALSE) %>%
  mutate(
      boot_d = map2(boot_d_scored, scale, function(x,y){filter_dscored(x, y)}),
      obs_changes = map(boot_d_scored, extract_obs_changes)
      ) %>%
  select(-boot_d_scored) %>%
  mutate(
    models = map2(boot_d, scale, function(x,y){add_evid_node(x, base_model, y)}),
    pred_changes = map(models, cogModel_predictions),
    r = map2_dbl(pred_changes, obs_changes, compare_pred_obs_r),
    rmse = map2_dbl(pred_changes, obs_changes, compare_pred_obs_rmse)
    )

print(Sys.time() - t1)
```

```{r}
# boot_fits %>%
#   mutate(r2 = r^2) %>%
#   ggplot(aes(x=reorder(scale,-r2), y = r2)) +
#   geom_boxplot(fill="lightgray") +
#   theme_bw() +
#   theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
#   coord_flip()
  # theme(axis.text.x = element_text(angle = 90, hjust = 1))

diagnose_plot <- boot_fits %>%
  select(replicate, scale,r,rmse) %>%
  mutate(scale_order = r) %>%
  gather(meas, value, r, rmse) %>%
  mutate(meas = ifelse(meas=="rmse", "RMSE (lower is better)", "Correlation")) %>%
  mutate(meas = factor(meas, levels=c("RMSE (lower is better)", "Correlation"))) %>%
  mutate(scale = recode_factor(
  scale,
  "vaccIntent" = "Vaccination Intentions",
  "nat" = "Naturalism",
  "hb" = "Holistic Balance",
  "overpar" = "Parental Protectiveness",
  "parentExpert" = "Parental Expertise",
  "medSkept" = "Medical Skepticism",
  "vaccDanger" = "Vaccine Danger",
  "vaccTox" = "Vaccine Toxicity",
  "vaccEff" = "Vaccine Efficacy",
  "diseaseRare" = "Disease Rarity",
  "diseaseSevere" = "Disease Severity",
  "infantImmWeak" = "IIS: Weakness",
  "infantImmLimCap" = "IIS: Limited Capacity",
  "vaccStrain" = "IIS: Vaccines Strain")) %>%
  ggplot(aes(x=reorder(scale, scale_order), y = value)) +
  # geom_violin(fill="gray", alpha=.5) +
  geom_boxplot(fill = "lightgray") +
  facet_wrap(~meas, scales="free_x" ) +
  labs(x = "Belief", y = "Value") +
  theme_bw(base_size=16) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  coord_flip()

ggsave("../local/uci-talk-diagnose.png",width=6,height=3.5)

diagnose_plot

>>>>

library(lubridate)

s4 <- df4 %>%
  mutate(prior_study = case_when(
    workerId %in% s1$workerId ~ "S1",
    workerId %in% s3$workerId ~ "S3",
    TRUE ~ "None"
  )) %>%
  mutate(resp = resp-4) %>%
  filter(prior_study != "S3", 
         StartDate < ymd_hms("2019-05-19:00:00:00")) %>% # exclude Ps from s3, some of whom saw intervention
  # filter(prior_study == "None") %>% # Look only at fresh Ps
  group_by(scale, workerId) %>%
  summarize(s4 = mean(resp))

s5 <- df4 %>%
  mutate(resp = resp-4) %>%
  filter(StartDate > ymd_hms("2019-05-19:00:00:00")) %>% # exclude Ps from s3, some of whom saw intervention
  # filter(prior_study == "None") %>% # Look only at fresh Ps
  group_by(scale, workerId) %>%
  summarize(s5 = mean(resp))
```

@@

df_studies <-  s1 %>%
  full_join(s2) %>%
  full_join(s3) %>%
  full_join(s4) %>%
  full_join(s5) %>%
  gather(study, score, -c(workerId, scale)) %>%
  filter(!is.na(study), !is.na(score)) %>%
  group_by(scale) %>%
  mutate(score_std = scale(score, scale = T)) %>%
  ungroup()
```

@@

```{r}
df_studies %>%
  group_by(study, scale) %>%
  summarize(
    mean = mean(score),
    se = sd(score)/sqrt(n()),
    ul = mean + se,
    ll = mean - se,
    ul95 = mean + 1.96*se,
    ll95 = mean - 1.96*se
  ) %>%
  ungroup() %>%
  mutate(study = ordered(study, 
                         labels=c("S1\n(9/'17)", 
                                  "S2\n(5/'18)", 
                                  "S3\n(4/'19)", 
                                  "S4\n(5/01)", 
                                  "S5\n(5/20)")
                         )
         ) %>%
  ggplot(aes(x=study, y = mean, ymin =ll, ymax=ul)) +
  geom_pointrange() +
  facet_wrap(~scale, scales="free") +
  theme_bw(base_size = 12) +
  labs(y="Mean Response", x = "Study")
```

```{r}
# important to recognize these are small changes in absolute terms ...
df_studies %>%
  ggplot(aes(x=study, y = score)) +
  geom_violin(fill = "blue",color="white",alpha=.5, scale="width", draw_quantiles=c(.5)) +
  facet_wrap(~scale, scales="free") +
  theme_bw()
```

@@

combined %>%
  filter(returned == TRUE) %>%
  ggplot(aes(x=pretest, y=posttest)) +
  geom_jitter(alpha=.5) +
  facet_wrap(~scale) +
  theme_bw()

@@

combined_long %>%
  group_by(returned, phase, scale) %>%
  summarize(
    mean = mean(resp),
    se = sd(resp)/sqrt(n()),
    ul = mean + se,
    ll = mean - se,
    ul95 = mean + 1.96*se,
    ll95 = mean - 1.96*se
  ) %>%
  ungroup() %>%
  mutate(phase = ordered(phase, levels=c("pretest","posttest"))) %>%
  ggplot(aes(x=phase, y = mean, ymin =ll, ymax=ul, color=returned)) +
  geom_point(position=position_dodge(width=.25), size=2, shape=16) +
  geom_errorbar(position=position_dodge(width=.25), size=.75, width=0, alpha=.8) +
  geom_errorbar(aes(ymin=ll95, ymax = ul95), width=0, position=position_dodge(width=.25), alpha=.5) +
  facet_wrap(~scale, scales="free") +
  theme_bw(base_size=18)

combined %>%
  filter(returned==TRUE) %>%
  mutate(diff = posttest-pretest) %>%
  group_by(scale) %>%
  summarize(
    mean = mean(diff),
    se = sd(diff)/sqrt(n()),
    ul = mean + se,
    ll = mean - se,
    ul95 = mean + 1.96*se,
    ll95 = mean - 1.96*se
  ) %>%
  ungroup() %>%
  # mutate(phase = ordered(phase, levels=c("pretest","posttest"))) %>%
  ggplot(aes(x=reorder(scale, mean), y = mean, ymin =ll, ymax=ul)) +
  geom_point(position=position_dodge(width=.25), size=2, shape=16) +
  geom_errorbar(position=position_dodge(width=.25), size=.75, width=0, alpha=.8) +
  geom_errorbar(aes(ymin=ll95, ymax = ul95), width=0, position=position_dodge(width=.25), alpha=.5) +
  geom_hline(yintercept = 0, linetype="dashed",alpha=.5) +
  # facet_wrap(~scale, scales="free") +
  theme_bw(base_size = 18) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  labs(y = "Change scores", x = "Belief scale")
```

```{r}
diff_df <- combined %>% 
  group_by(scale) %>% 
  summarize(posttest = mean(posttest, na.rm=TRUE), 
            pretest=mean(pretest)) %>% 
  mutate(diff = posttest-pretest)

@@

change_cors %>%
  ggplot(aes(y=reorder(scale, corr), x = corr)) +
  geom_point() +
  theme_bw(base_size=18) +
  theme(aspect.ratio=1) +
  labs(y="Scale", x = "Correlation")
```

@@

z %>%
  ggplot(aes(x=pred_diff, y=diff)) +
  geom_point() +
  theme_bw(base_size=18) +
  theme(aspect.ratio=1) +
  labs(x="Predicted change",y="Observed change", title=targetted_belief)

cor(z$pred_diff, z$diff)
```

@@

# insepcting other ps

For some reason our "fresh" participants don't look quite like our S1 and S3 participants. A difference between S3 participants seems plausible, but I don't see how they could meaningfully differ from S1 participants beyond by chance. I say that especially because returning and non-returning participants from S1 didn't look different across any of the scales.

```{r}
df4 %>%
  mutate(prior_study = case_when(
    workerId %in% s1$workerId ~ "S1",
    workerId %in% s3$workerId ~ "S3",
    TRUE ~ "None"
  )) %>%
  mutate(resp = resp-4) %>%
  # filter(prior_study != "S3") %>% # exclude Ps from s3, some of whom saw intervention
  group_by(prior_study,scale, workerId) %>%
  summarize(s4 = mean(resp)) %>%
  group_by(prior_study, scale) %>%
  summarize(Mean = mean(s4, na.rm=TRUE)) %>%
  spread(prior_study, Mean)
```

### 2019-08-08 notebooks/s2-analysis.Rmd
before paper reorg

```{r setup, include = F}
library(tidyverse)
library(psych)
# library(ggcorrplot)
library(lme4)
library(brms)
library(rms)

```

@@

g_diffs <- ggplot(d_diffs,
                  aes(x = scale, y = Mean, 
                      color = condition, group = condition)) +
  # facet_wrap(~ scale, ncol = 3) +
  geom_hline(yintercept = 0, lty = 2, size = 0.5) +
  geom_linerange(aes(ymin = Lower, ymax = Upper)) +
  geom_point(size = 3) +
  scale_y_continuous("mean diff") + #, 
                     # limits = c(-3, 3), 
                     # breaks = seq(-3, 3, 1)) +
  scale_color_brewer(palette = "Set1", direction = -1) +
  theme_bw() +
  theme(
    # legend.position = "none",
        axis.text.x = element_text(angle = 90, hjust = 1)) +
  labs(title = "mean difference scores by scale and condition",
       subtitle = "error bars are 95% bootstrapped CIs")

@@

```{r}
library(betareg)

>>>>

```{r setup, include = F}
library(tidyverse)
library(psych)
library(lme4)
library(brms)
library(Hmisc)

if require(betareg)
```

@@

g_diffs <- ggplot(d_diffs,
                  aes(x = reorder(scale, -Mean), y = Mean, 
                      color = condition, group = condition)) +
  # facet_wrap(~ scale, ncol = 3) +
  geom_hline(yintercept = 0, lty = 2, size = 0.5) +
  geom_linerange(aes(ymin = Lower, ymax = Upper)) +
  geom_point(size = 3) +
  scale_y_continuous("mean diff") + #, 
                     # limits = c(-3, 3), 
                     # breaks = seq(-3, 3, 1)) +
  scale_color_brewer(palette = "Set1", direction = -1) +
  theme_bw() +
  theme(
    # legend.position = "none",
        axis.text.x = element_text(angle = 90, hjust = 1)) +
  labs(title = "mean difference scores by scale and condition",
       subtitle = "error bars are 95% bootstrapped CIs")

@@

### 2019-08-08 notebooks/s2-modeling.Rmd
modeling updates
before paper reorg

```{r load in existing objects, message=FALSE, warning=FALSE}
# net.struct <- readRDS("net-struct-cogsci2018.rds")

@@

library(rsample)

@@

ggsave("../local/obs_pred_plot.png",obs_pred_plot)
```

>>>>

```{r load in existing objects, message=FALSE, warning=FALSE}
# # install missing packages
devtools::install_github("thomasp85/patchwork")
install.packages("rsample")

@@

# library(rsample)

@@

# ggsave("../local/obs_pred_plot.png",obs_pred_plot)
```
